Precise Weed and Maize classification through Convolutional Neuronal Networks

### 2017-07-21 PaperBCJ.tex
Cambios20jul
cambios hasta las 22:00pm

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Andrea Concepci\'on C\'ordova Cruzatty \IEEEauthorrefmark{1},
Mauricio Daniel Barreno Barreno \IEEEauthorrefmark{2} and Jos\'e Misael J\'acome Barrionuevo\IEEEauthorrefmark{3}}
\IEEEauthorblockA{Department of Energy and Mechanics,
University of the Army ESPE\\
Latacunga - Quijano y Ordo\~nez and Hermanas Pa\'ez \\
Email: \IEEEauthorrefmark{1}accordova@espe.edu.ec,
\IEEEauthorrefmark{2}mdbarreno@espe.edu.ec,
\IEEEauthorrefmark{3}jmjacome1@espe.edu.ec}}
% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

@@

Deep Learning has played a very important role in modern times, being very used in Artificial Vision and especially in Pattern Recognition, which opens many doors in the fields of application among which is precision agriculture. In this paper the study of a convolutional neural network is presented, with two classes applied to the classification of plants of maize and weeds in real time, focused to fields of maize in its initial stage. The algorithm has two stages, segmentation of images and classification. Segmentation is intended to separate the target plant from the original image. While the classification is possible through a convolutional neural network, previously trained with a dataset generated through the segmentation stage. The performance of the network is illustrated by analysis and comparisons with different network architectures, then with the network that presented better results in training, (revisar esta linea) we experimented by modifying its number of filters, to analyze their behavior. Finally, the resulting network was tested on different processors to compare classification times.\\

@@

-El uso de Multithreading y Batching a traves de la libreria OpenBLAS es muy beneficioso en el caso de usar CPU, aumentando la rapidez de procesamiento en el porcentaje superior al 20\%, con la Rasberry pi, se obtuvo una minima mejora, en cambio fue pejudicial con el uso de GPU , pues provoca que la rapidez se reduzca considerablemente. \\

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Andrea C\'ordova-Cruzatty \IEEEauthorrefmark{1},
Mauricio Daniel Barreno Barreno \IEEEauthorrefmark{2} and Jos\'e Misael J\'acome Barrionuevo\IEEEauthorrefmark{3}}
\IEEEauthorblockA{Department of Energy and Mechanics,
University of the Army ESPE\\
Latacunga - Quijano y Ordo\~nez and Hermanas Pa\'ez \\
Email: \IEEEauthorrefmark{1}accordova@espe.edu.ec,
\IEEEauthorrefmark{2}mdbarreno@espe.edu.ec,
\IEEEauthorrefmark{3}jmjacome1@espe.edu.ec}}
% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

@@

Deep Learning has played an important role in modern times, being widely used in artificial vision applications and specifically in pattern recognition. The versatility of deep learning has positioned it as a fit tool used in many fields of application, among which is precision agriculture. This paper presents a study of a convolutional neural network with two classes, applied for the classification between maize plants and weeds in real time, focused on maize crops in their initial development stages. The algorithm has two stages, segmentation of images and classification. Segmentation is intended to separate the target plant from the original image. While the classification is possible through a convolutional neural network, previously trained with a dataset generated through the segmentation stage. The performance of the network is illustrated by analysis and comparisons with different network architectures, then with the network that presented better results in training, (revisar esta linea) we experimented by modifying its number of filters, to analyze their behavior. Finally, the resulting network was tested on different processors to compare classification times.\\

@@

\begin{comment}
-El uso de Multithreading y Batching a traves de la libreria OpenBLAS es muy beneficioso en el caso de usar CPU, aumentando la rapidez de procesamiento en el porcentaje superior al 20\%, con la Rasberry pi, se obtuvo una minima mejora, en cambio fue pejudicial con el uso de GPU , pues provoca que la rapidez se reduzca considerablemente. \\
\end{comment}
